Secure Composition \\ of Robust and Optimising Compilers

### 2023-10-09 esop/main.tex
space + font

\usepackage[T1]{fontenc}

@@

% \author{
% Matthis Kruse\orcidID{0000-0003-4062-9666}
% \and
% Michael Backes
% \and
% Marco Patrignani
% }
% \authorrunning{M. Kruse et al.}

% \institute{
% CISPA Helmholtz Center for Information Security and Saarland University
% \and
% CISPA Helmholtz Center for Information Security
% \and
% Trento University
% }

@@

\begin{definition}[Robust Satisfaction]\label{def:proprsat}
  \begin{nscenter}
  \bul{$\rsat{\progvar}{\pi}$}
  $\isdef$ \iul{$\forall \contextvar\ \wholeprogvar$, if $\link{\contextvar}{\progvar}=\wholeprogvar$}, then \oul{$\sat{\wholeprogvar}{\pi}$}.
  \end{nscenter}
\end{definition}

@@

\begin{definition}[Robust Compilation]\label{def:rtp}
  $\;$\\
  \vspace{-1em}
  \begin{nscenter}
  % Compiler $\cc{\src{L}}{\trg{L}}$ robustly preserves $\class$, 
  \bul{$\rtp{\cc{\src{L}}{\trg{L}}}{\class}$}
  %, iff 
  $\isdef$
  \rul{$\forall \pi\in\class, \src{p}\in\src{L},$} if \iul{$\rsat{\src{\progvar}}{\pi}$}, then \oul{$\rsat{\cc{\src{L}}{\trg{L}}\left(\src{p}\right)}{\pi}$}.
  \end{nscenter}
\end{definition}

Note that a class of properties $\class$ can represent just one property $\pi$ by lifting~\cite{clarkson2008hyper} that property to sets of properties, i.e., use the powerset of $\pi$ instead of $\pi$ itself.
Thus we write $\rtp{\cc{\src{L}}{\trg{L}}}{\pi}$, even though $\pi$ is a property and not a class.
% \MP{
% 	check that we say classes are hp
% }

@@

\begin{definition}[\glsfirst*{sms}]\label{def:trace:smsdef}
\small
  $
  \smssafe:=\left\{\trace \left|\begin{array}{rcl}
                                  \text{If }\ev{Alloc\ \loc\ n;\sandboxtag;\securitytag}\le_{\trace}\ev{Use\ \loc\ m;\sandboxtag;\securitytag'}, \text{ then }m<n
                                \end{array}\right.\right\}
  $
\end{definition}

@@

\begin{definition}[\glsfirst*{scct}]\label{def:trace:scctdef}
  $
  \scctsafe:=\left\{\trace \left|\begin{array}{rcl}
                                   \trace=\hole{\cdot} & \text{ or } & \trace=\event[_{b}];\sandboxtag;\unlock\cdot\trace['] \wedge \trace[']\in\scctsafe
                                 \end{array}\right.\right\}
  $
\end{definition}

@@

\subsubsection{Monitor for \glsfirst*{tms}}\label{subsubsec:tms}
\begin{gather*}
  \begin{aligned}
    \mi{(Abstract\ Store)}~\tmsmonitor\bnfdef&\ \left\{\text{A}:L\times\sandboxtag,\text{F}:L\times\sandboxtag\right\} 
    \\%
    % \emptyset:=&\ \left\{\text{A}:\emptyset,\text{F}:\emptyset\right\}
    % \\
    \mi{(Abstract\ Events)}~\absevent\bnfdef&\ \absev{\emptyevent} \mid \absev{Alloc\ }\loc\ \sandboxtag \mid \absev{Dealloc\ }\loc\ \sandboxtag \\
                                            & \mid \absev{Use\ }\loc\ \sandboxtag \mid \absterm\\
  \end{aligned}
\end{gather*}
For \gls*{tms}, the state of the monitor is a record with two sets keeping track of allocated and deallocated locations, and the initial state $\emptyset$ is defined as $\left\{\text{A}:\emptyset,\text{F}:\emptyset\right\}$.
% 
Monitor events include {\em allocation}, {\em deallocation}, and {\em use} of a location $\loc$ as well as abnormal program termination.

\begin{center}\small
  \judgbox{\monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absevent}}{,,Monitor $\tmsmonitor$ steps to $\tmsmonitor[']$ given event $\absevent$.''}$\;$\\
  %
% \typerule{tms-uninteresting}{
% }{
%   \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absev{\emptyevent}}
% }{tms-uninteresting}
% %
% \typerule{tms-abort}{
% }{
%   \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absterm}
% }{tms-abort}
  % 
  \typerule{tms-use}{
    (\loc;\sandboxtag)\in\tmsmonitor.\text{A} 
    &
    % \\
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{F}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absev{Use\ }\loc\ \sandboxtag}
  }{tms-use}
  %
  \typerule{tms-alloc}{
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{A} &
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{F} \\
    \tmsmonitor[']=\left\{\text{A}: \tmsmonitor.\text{A}\cup\left\{(\loc;\sandboxtag)\right\},\text{F}: \tmsmonitor.\text{F}\right\}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{Alloc\ }\loc\ \sandboxtag}
  }{tms-alloc}
  %
  \typerule{tms-dealloc}{
    (\loc;\sandboxtag)\in\tmsmonitor.\text{A} 
    &
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{F} 
    \\
    \tmsmonitor[']=\left\{\text{A}: \tmsmonitor.\text{A}\setminus\left\{(\loc;\sandboxtag)\right\} \text{F}: \tmsmonitor.\text{F}\cup\left\{(\loc;\sandboxtag)\right\}\right\}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{Dealloc\ }\loc\ \sandboxtag}
  }{tms-dealloc}
  %
\end{center}

@@

  \vspace{-1em}
  {\small
  \begin{align*}
   	% \abstrace=
   	&
   	\absev{Alloc}\ \loc[_{x}]\ \comp
   	\cdot
   	\absev{Alloc}\ \loc[_{y}]\ \comp
   	\cdot
   	\absev{Use}\ \loc[_{x}]\ \comp
   	\\
   	&
   	\cdot
   	\absev{Use}\ \loc[_{x}]\ \comp
   	\cdot
   	\absev{Use}\ \loc[_{y}]\ \comp
   	\cdot
   	\ldots
   	\\
   	&
   	\cdot
   	\absev{Use}\ \loc[_{x}]\ \comp
   	\cdot
   	\absev{Dealloc}\ \loc[_{y}]\ \comp
   	\cdot
   	\absev{Use}\ \loc[_{y}]\ \comp
   \end{align*} 
  	}
  Remembering the definition of \texttt{strncpy} (\Cref{ex:strncpy}), observe that it does not deallocate its arguments.
  Even though the trace contains an out-of-bounds access right before returning from \texttt{strncpy}, this is no concern for \gls*{tms}, since location $\loc[_{x}]$ is still allocated.
  Having returned from \texttt{strncpy}, the \texttt{greet} function continues and deallocates $\loc[_{y}]$ whose subsequent use in \texttt{printf} is a use-after-free bug.

@@

\vspace{-1em}
  {\small
  \begin{align*}
  	\abstrace[']=
  	&
  	\absev{Alloc}\ \loc[_{x}]\ \comp
  	\cdot
  	\absev{Alloc}\ \loc[_{y}]\ \comp
  	\cdot
  	\absev{Use}\ \loc[_{x}]\ \comp
  	\\
  	&
  	\cdot
  	\absev{Use}\ \loc[_{x}]\ \comp
  	\cdot
  	\absev{Use}\ \loc[_{y}]\ \comp
  	\cdot
  	\ldots
  	\cdot
  	\\
  	&
  	\absev{Use}\ \loc[_{x}]\ \comp
  	\cdot
  	\absev{Dealloc}\ \loc[_{x}]\ \comp
  	\cdot
  	\absev{Use}\ \loc[_{y}]\ \comp	
  \end{align*}
  }
  It follows that $\montmssafe{\abstrace[']}$ and from \Thmref{lem:mon:tmssafe}, it follows that the program satisfies \Thmref{def:trace:tmsdef}, even though the program still violates \gls*{sms}.
\end{exampleenv}

@@

  	{\small
  	\begin{align*}
  	&
  		\ldots
  		\cdot
  		\ev{Alloc}\ \loc_{x}\ 2;\comp;\unlock
  		\cdot
  		\ldots
  		\cdot
  		\ev{Alloc}\ \loc_{y}\ 2;\comp;\unlock
  		\cdot
  		\ldots
  		\cdot
  	\\
  	&
  		\ev{Use}\ \loc_{x}\ 0;\comp;\unlock
  		\cdot
  		\ev{Use}\ \loc_{y}\ 0;\comp;\unlock
  		\cdot
  		\ev{Use}\ \loc_{x}\ 1;\comp;\unlock
  	\\
  	&
  		\cdot
  		\ev{Use}\ \loc_{y}\ 1;\comp;\unlock
  		\cdot
  		\ev{Use}\ \loc_{x}\ 2;\comp;\unlock
  		\cdot
  		\ldots	
  	\end{align*}
  	}

\noindent
where $\loc_{x}$ and $\loc_{y}$ are the memory addresses associated to \texttt{x} and \texttt{y}, respectively.
  Omitting the events for all ,,$\ldots$'' for sake of brevity, the abstract monitor trace of this is:

  	{\small
  	\begin{align*}
  		&
  		\absev{Alloc}\ \loc_{x}\ \comp\ 2
  		\cdot
  		\absev{Alloc}\ \loc_{y}\ \comp\ 2
  		\cdot
  		\absev{Use}\ \loc_{x}\ \comp\ 0
  		\\
  		&
  		\cdot
  		\absev{Use}\ \loc_{y}\ \comp\ 0
  		\cdot
  		\absev{Use}\ \loc_{x}\ \comp\ 1
  		\cdot
  		\absev{Use}\ \loc_{y}\ \comp\ 1
  		\cdot
  		\absev{Use}\ \loc_{x}\ \comp\ 2
  	\end{align*}
  	}

@@

\vspace{-1em}
  {\small
  \begin{align*}
  	\ev{Use}\ \loc_{x}\ 0;\comp;\unlock\cdot\ev{Use}\ \loc_{y}\ 0;\comp;\lock	
  \end{align*}
  }
  In terms of the abstract monitor trace, this is just $\absev{Leak}$.
  Running this on the monitor would result in getting stuck, since there is no matching rule to step in the presence of $\absev{Leak}$ event. % pun intended
  By means of additional features to ensure cryptographic constant time even in the presence of memory reads and loads, such as a flag to enable a data independent timing mode, which is present in both Arm~\cite[p.~543]{arm-refman} and Intel~\cite[p.~80]{intel-refman} processors, the original trace now does $\ev{Use}\ \loc_{y}\ 0;\comp;\unlock$ instead of $\ev{Use}\ \loc_{y}\ 0;\comp;\lock$.
  Because of this, the whole trace of the component equates to $\absev{\emptyevent}$ and the monitor can step without getting stuck.
\end{exampleenv}

@@

\begin{lemma}[Monitor Satisfaction is $\msscctsafe$]\label{lem:mon:msscctsafe}
  $\;$\\\vspace{-1em}
  \begin{nscenter}
  If $\monmsscctsafe{\trace}$, then $\trace\in\msscctsafe$. %\Coqed
  \end{nscenter}
\end{lemma}

@@

With this, \bul{a cross-language relation $\sim$ is well-formed with respect to a class of source-level properties $\src{\class}$} iff \rul{the existential images preserve set inclusion}.
\begin{definition}[Well-formedness of Trace Relations for a Class $\src{\class}$]\label{def:wfc:tracerel}
  $$
  \text{\bul{$\wfc{\sim}{\src{\class}}$}} \isdef \text{\rul{$\forall \src{\Pi}\subseteq\src{\class}, \tau_\sim(\src{\Pi})\subseteq\tilde{\tau}_\sim(\src{\class})$}}
  $$
\end{definition}

@@

\begin{definition}[Robust Compilation with $\sim$]\label{def:rtpsim}
  $$\rtpsim{\cc{\src{L}}{\trg{L}}}{\src{\class}}{\sim} \isdef
  \forall \src{\pi} \src{p}.
    \text{if }\rsat{\src{\progvar}}{\src{\pi}},
    \text{then }\rsat{\cc{\src{L}}{\trg{L}}\left(\src{p}\right)}{\tilde{\tau}_\sim\left(\src{\pi}\right)}.
  $$
\end{definition}

@@

\vspace{-1em}
\begin{center}\small
  $$
  \begin{array}{rcl}
    \ccb(\trg{\lnew{x}{\expr[_{1}]}{\expr[_{2}]}}) & = & \llet[\irl]{\irl{x_{SIZE}}}{\ccb(\trg{\expr[_{1}]})}{\\&&\lnew[\irl]{\irl{x}}{\irl{x_{SIZE}}}{\ccb(\trg{\expr[_{2}]})}} \\
  \ccb(\trg{\lget{x}{\expr}}) & = & \llet[\irl]{\irl{x_{n}}}{\ccb(\trg{\expr})}{\\&&\lifz[\irl]{\irl{0\le x_{n}<x_{SIZE}}}{\irl{\lget{x}{x_{n}}}}{\\&&\irl{\labort}}} \\
  \ccb(\trg{\lset{x}{\expr[_{1}]}{\expr[_{2}]}}) & = & \llet[\irl]{\irl{x_{n}}}{\ccb(\trg{\expr[_{1}]})}{\\&&\lifz[\irl]{\irl{0\le x_{n}<x_{SIZE}}}{\lset[\irl]{\irl{x}}{\irl{x_{n}}}{\\&&\ccb(\trg{\expr[_{2}]})}}{\irl{\labort}}} \\
  \end{array}
  $$
\end{center}

>>>>

\usepackage[T1]{fontenc}
\usepackage[scaled=.83]{beramono}

@@

\author{}
% Matthis Kruse\orcidID{0000-0003-4062-9666}
% \and
% Michael Backes
% \and
% Marco Patrignani
% }
% \authorrunning{M. Kruse et al.}

\institute{}
% CISPA Helmholtz Center for Information Security and Saarland University
% \and
% CISPA Helmholtz Center for Information Security
% \and
% Trento University
% }

@@

\begin{definition}[Robust Satisfaction]\label{def:proprsat}
  % \begin{nscenter}
  \bul{$\rsat{\progvar}{\pi}$}
  $\isdef$ \iul{$\forall \contextvar\ \wholeprogvar$, if $\link{\contextvar}{\progvar}=\wholeprogvar$}, then \oul{$\sat{\wholeprogvar}{\pi}$}.
  % \end{nscenter}
\end{definition}

@@

\begin{definition}[Robust Compilation]\label{def:rtp}
  % $\;$\\
  % \vspace{-1em}
  % \begin{nscenter}
  % Compiler $\cc{\src{L}}{\trg{L}}$ robustly preserves $\class$, 
  \bul{$\rtp{\cc{\src{L}}{\trg{L}}}{\class}$}
  %, iff 
  $\isdef$
  \rul{$\forall \pi\in\class, \src{p}\in\src{L},$} if \iul{$\rsat{\src{\progvar}}{\pi}$}, then \oul{$\rsat{\cc{\src{L}}{\trg{L}}\left(\src{p}\right)}{\pi}$}.
  % \end{nscenter}
\end{definition}
% 
Note that a class of properties $\class$ can represent just one property $\pi$ by lifting~\cite{clarkson2008hyper} that property to sets of properties, i.e., use the powerset of $\pi$ instead of $\pi$ itself.
Thus we write $\rtp{\cc{\src{L}}{\trg{L}}}{\pi}$, even though $\pi$ is a property and not a class.
% \MP{
% 	check that we say classes are hp
% }

@@

\begin{definition}[\glsfirst*{sms}]\label{def:trace:smsdef}
% \small
  % \begin{nscenter}

  \noindent
  $
  \smssafe:=\left\{\trace \left|\begin{array}{rcl}
                                  \text{If }\ev{Alloc\ \loc\ n;\sandboxtag;\securitytag}\le_{\trace}\ev{Use\ \loc\ m;\sandboxtag;\securitytag'}, \text{ then }m<n
                                \end{array}\right.\right\}
                                $
  % \end{nscenter}
\end{definition}

@@

\begin{definition}[\glsfirst*{scct}]\label{def:trace:scctdef}
% \begin{nscenter}

  \noindent$
  \scctsafe:=\left\{\trace \left|\begin{array}{rcl}
                                   \trace=\hole{\cdot} & \text{ or } & \trace=\event[_{b}];\sandboxtag;\unlock\cdot\trace['] \wedge \trace[']\in\scctsafe
                                 \end{array}\right.\right\}
  $
% \end{nscenter}
\end{definition}

@@

\subsubsection{Monitor for \glsfirst*{tms}}\label{subsubsec:tms}
\begin{gather*}
  \begin{aligned}
    \mi{(Abstract\ Store)}~\tmsmonitor\bnfdef&\ \left\{\text{A}:L\times\sandboxtag,\text{F}:L\times\sandboxtag\right\} 
    \\%
    % \emptyset:=&\ \left\{\text{A}:\emptyset,\text{F}:\emptyset\right\}
    % \\
    \mi{(Abstract\ Events)}~\absevent\bnfdef&\ \absev{\emptyevent} \mid \absev{Alloc\ }\loc\ \sandboxtag \mid \absev{Dealloc\ }\loc\ \sandboxtag 
    % \\
                                            % & 
                                            \mid \absev{Use\ }\loc\ \sandboxtag \mid \absterm\\
  \end{aligned}
\end{gather*}
For \gls*{tms}, the state of the monitor is a record with two sets keeping track of allocated and deallocated locations, and the initial state $\emptyset$ is defined as $\left\{\text{A}:\emptyset,\text{F}:\emptyset\right\}$.
% 
Monitor events include {\em allocation}, {\em deallocation}, and {\em use} of a location $\loc$ as well as abnormal program termination.

\begin{center}\small
  \judgbox{\monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absevent}}{,,Monitor $\tmsmonitor$ steps to $\tmsmonitor[']$ given event $\absevent$.''}$\;$\\
  %
% \typerule{tms-uninteresting}{
% }{
%   \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absev{\emptyevent}}
% }{tms-uninteresting}
% %
% \typerule{tms-abort}{
% }{
%   \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absterm}
% }{tms-abort}
  % 
  \typerule{tms-use}{
    (\loc;\sandboxtag)\in\tmsmonitor.\text{A} 
    &
    % \\
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{F}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absev{Use\ }\loc\ \sandboxtag}
  }{tms-use}
  %
  \typerule{tms-alloc}{
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{A} &
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{F} 
    % \\
    &
    \tmsmonitor[']=\left\{\text{A}: \tmsmonitor.\text{A}\cup\left\{(\loc;\sandboxtag)\right\},\text{F}: \tmsmonitor.\text{F}\right\}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{Alloc\ }\loc\ \sandboxtag}
  }{tms-alloc}
  %
  \typerule{tms-dealloc}{
    (\loc;\sandboxtag)\in\tmsmonitor.\text{A} 
    &
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{F} 
    \\
    \tmsmonitor[']=\left\{\text{A}: \tmsmonitor.\text{A}\setminus\left\{(\loc;\sandboxtag)\right\} \text{F}: \tmsmonitor.\text{F}\cup\left\{(\loc;\sandboxtag)\right\}\right\}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{Dealloc\ }\loc\ \sandboxtag}
  }{tms-dealloc}
  %
\end{center}

@@

  \vspace{-1em}
  {\small
  \begin{align*}
   	% \abstrace=
   	&
   	\absev{Alloc}\ \loc[_{x}]\ \comp
   	\cdot
   	\absev{Alloc}\ \loc[_{y}]\ \comp
   	\cdot
   	\absev{Use}\ \loc[_{x}]\ \comp
   	% \\
   	% &
   	\cdot
   	\absev{Use}\ \loc[_{x}]\ \comp
   	\cdot
   	\absev{Use}\ \loc[_{y}]\ \comp
   	\cdot
   	\ldots
   	\\
   	&
   	\cdot
   	\absev{Use}\ \loc[_{x}]\ \comp
   	\cdot
   	\absev{Dealloc}\ \loc[_{y}]\ \comp
   	\cdot
   	\absev{Use}\ \loc[_{y}]\ \comp
   \end{align*} 
  	}
  Remembering the definition of \texttt{strncpy} (\Cref{ex:strncpy}), observe that it does not deallocate its arguments.
  Even though the trace contains an out-of-bounds access right before returning from \texttt{strncpy}, this is no concern for \gls*{tms}, since location $\loc[_{x}]$ is still allocated.
  Having returned from \texttt{strncpy}, the \texttt{greet} function continues and deallocates $\loc[_{y}]$ whose subsequent use in \texttt{printf} is a use-after-free bug.

@@

\vspace{-1em}
  {\small
  \begin{align*}
  	\abstrace[']=
  	&
  	\absev{Alloc}\ \loc[_{x}]\ \comp
  	\cdot
  	\absev{Alloc}\ \loc[_{y}]\ \comp
  	\cdot
  	\absev{Use}\ \loc[_{x}]\ \comp
  	% \\
  	% &
  	\cdot
  	\absev{Use}\ \loc[_{x}]\ \comp
  	\cdot
  	\absev{Use}\ \loc[_{y}]\ \comp
  	\cdot
  	\ldots
  	\cdot
  	\\
  	&
  	\absev{Use}\ \loc[_{x}]\ \comp
  	\cdot
  	\absev{Dealloc}\ \loc[_{x}]\ \comp
  	\cdot
  	\absev{Use}\ \loc[_{y}]\ \comp	
  \end{align*}
  }
  It follows that $\montmssafe{\abstrace[']}$ and from \Thmref{lem:mon:tmssafe}, it follows that the program satisfies \Thmref{def:trace:tmsdef}, even though the program still violates \gls*{sms}.
\end{exampleenv}

@@

  	{\small
  	\begin{align*}
  	&
  		\ldots
  		\cdot
  		\ev{Alloc}\ \loc_{x}\ 2;\comp;\unlock
  		\cdot
  		\ldots
  		\cdot
  		\ev{Alloc}\ \loc_{y}\ 2;\comp;\unlock
  		\cdot
  		\ldots
  		\cdot
  	% \\
  	% &
  		\ev{Use}\ \loc_{x}\ 0;\comp;\unlock
  		\cdot
  		\\
  	&
  		\ev{Use}\ \loc_{y}\ 0;\comp;\unlock
  		\cdot
  		\ev{Use}\ \loc_{x}\ 1;\comp;\unlock
  	% \\
  	% &
  		\cdot
  		\ev{Use}\ \loc_{y}\ 1;\comp;\unlock
  		\cdot
  		\ev{Use}\ \loc_{x}\ 2;\comp;\unlock
  		\cdot
  		\ldots	
  	\end{align*}
  	}

\noindent
where $\loc_{x}$ and $\loc_{y}$ are the memory addresses associated to \texttt{x} and \texttt{y}, respectively.
  Omitting the events for all ,,$\ldots$'' for sake of brevity, the abstract monitor trace of this is:
  	% 
  	{\small
  	\begin{align*}
  		&
  		\absev{Alloc}\ \loc_{x}\ \comp\ 2
  		\cdot
  		\absev{Alloc}\ \loc_{y}\ \comp\ 2
  		\cdot
  		\absev{Use}\ \loc_{x}\ \comp\ 0
  		\\
  		&
  		\cdot
  		\absev{Use}\ \loc_{y}\ \comp\ 0
  		\cdot
  		\absev{Use}\ \loc_{x}\ \comp\ 1
  		\cdot
  		\absev{Use}\ \loc_{y}\ \comp\ 1
  		\cdot
  		\absev{Use}\ \loc_{x}\ \comp\ 2
  	\end{align*}
  	}

@@

\vspace{-1em}
  {\small
  \begin{align*}
  	\ev{Use}\ \loc_{x}\ 0;\comp;\unlock\cdot\ev{Use}\ \loc_{y}\ 0;\comp;\lock	
  \end{align*}
  }
  In terms of the abstract monitor trace, this is just $\absev{Leak}$.
  Running this on the monitor would result in getting stuck, since there is no matching rule to step in the presence of $\absev{Leak}$ event. % pun intended
  By means of additional features to ensure cryptographic constant time even in the presence of memory reads and loads, such as a flag to enable a data independent timing mode, which is present in both Arm~\cite[p.~543]{arm-refman} and Intel~\cite[p.~80]{intel-refman} processors, the original trace now does $\ev{Use}\ \loc_{y}\ 0;\comp;\unlock$ instead of $\ev{Use}\ \loc_{y}\ 0;\comp;\lock$.
  Because of this, the whole trace of the component is $\absev{\emptyevent}$ and the monitor can step without getting stuck.
\end{exampleenv}

@@

\begin{lemma}[Monitor Satisfaction is $\msscctsafe$]\label{lem:mon:msscctsafe}
  % $\;$\\\vspace{-1em}
  % \begin{nscenter}
  % \noindent
  If $\monmsscctsafe{\trace}$, then $\trace\in\msscctsafe$. %\Coqed
  % \end{nscenter}
\end{lemma}

@@

With this, \bul{a cross-language relation $\sim$ is well-formed with respect to a class of source-level properties $\src{\class}$} iff \rul{the existential images preserve set inclusion}.
\begin{definition}[Well-formedness of Trace Relations for a Class $\src{\class}$]\label{def:wfc:tracerel}
  % $$

  \noindent
  \text{\bul{$\wfc{\sim}{\src{\class}}$}} \isdef \text{\rul{$\forall \src{\Pi}\subseteq\src{\class}, \tau_\sim(\src{\Pi})\subseteq\tilde{\tau}_\sim(\src{\class})$}}
  % $$
\end{definition}

@@

\begin{definition}[Robust Compilation with $\sim$]\label{def:rtpsim}
  $
  \rtpsim{\cc{\src{L}}{\trg{L}}}{\src{\class}}{\sim} \isdef
  \forall \src{\pi} \src{p}.
    \text{if }\rsat{\src{\progvar}}{\src{\pi}},
    \text{then }\rsat{\cc{\src{L}}{\trg{L}}\left(\src{p}\right)}{\tilde{\tau}_\sim\left(\src{\pi}\right)}.
  $
\end{definition}

@@

\vspace{-1em}
\begin{center}\small
  $$
  \begin{array}{rcl}
    \ccb(\trg{\lnew{x}{\expr[_{1}]}{\expr[_{2}]}}) & = 
    	& \llet[\irl]{\irl{x_{SIZE}}}{\ccb(\trg{\expr[_{1}]})}{
    		% \\&&
    		\lnew[\irl]{\irl{x}}{\irl{x_{SIZE}}}{\ccb(\trg{\expr[_{2}]})}
    		} \\
  \ccb(\trg{\lget{x}{\expr}}) & = 
  	& \llet[\irl]{\irl{x_{n}}}{\ccb(\trg{\expr})}{
  	% \\&&
  	\lifz[\irl]{\irl{0\le x_{n}<x_{SIZE}}}{\irl{\lget{x}{x_{n}}}}{
  		% \\&&
  		\irl{\labort}
  		}
  		} \\
  \ccb(\trg{\lset{x}{\expr[_{1}]}{\expr[_{2}]}}) & = 
  	& \llet[\irl]{\irl{x_{n}}}{\ccb(\trg{\expr[_{1}]})}{
  		\\&&
  		\lifz[\irl]{\irl{0\le x_{n}<x_{SIZE}}}{\lset[\irl]{\irl{x}}{\irl{x_{n}}}{
  		% \\&&
  		\ccb(\trg{\expr[_{2}]})
  		}}{\irl{\labort}}
  		} 
  		% \\
  \end{array}
  $$
\end{center}
